%
%
% report_2025_1_intro.tex
%
%
%
\documentclass[jctc-draft.tex]{subfiles}
\begin{document}
\section{Introduction}
Since the early conception of quantum computers, quantum chemistry simulation
has been recognized as a highly promising application area expected to be
significantly advanced by quantum computing
\cite{Cao2019.doi:10.1021/acs.chemrev.8b00803}. Currently, mainstream quantum
hardware is inherently prone to computational errors due to noise, and the
practical implementation of error correction technologies is ongoing. The
surface code method, a promising error correction technique for quantum
computers, requires a significantly higher level of redundancy compared to
classical error correction methods \cite{Fowler2012.PhysRevA.86.032324}.
Consequently, realizing a practical fault-tolerant quantum computer (FTQC) faces
implementation challenges, primarily the need to vastly increase the number of
qubits on hardware devices, and is expected to take several more years. In the
current Noisy Intermediate-Scale Quantum (NISQ) era, where error correction is
not yet implemented and qubit counts are limited, Variational Quantum
Eigensolver (VQE)-based algorithms utilizing second quantization are the
mainstream of quantum chemistry research \cite{peruzzo2014variational}. VQE
combines a quantum computer with a classical computer to reduce the required
number of qubits and circuit depth, making it executable on NISQ devices as it
can tolerate the presence of noise. However, once FTQC is realized---mitigating
the impact of noise and relaxing qubit constraints---a broader range of algorithms
is expected to be researched and put into practical use.

The grid-based approach, a representative method for quantum chemistry
simulation based on first quantization, is one of the ultimate targets in this
field because it can directly handle electron interactions without depending on
the choice of basis functions. However, it requires more computational resources
than VQE \cite{kassal2008.pnas.0808245105}. In the grid method, the indices of
equally spaced grid points are mapped to the basis states of a qubit register,
and the wave function's amplitude at each grid point is stored as the register's
amplitude to calculate the time evolution of the wave function. While algorithms
based on the Suzuki-Trotter decomposition are widely known for time evolution
calculations, algorithms employing more sophisticated approaches have also been
proposed \cite{Berry2015.PhysRevLett.114.090502, Babbush_2018c,
YuanSu.PRXQuantum.2.040332}. Nevertheless, because all of these grid-based
algorithms generally require a large number of qubits and significant circuit
depth, and cannot tolerate computational errors, reports of their operational
verification are strictly limited. To the best of the authors' knowledge, no
calculations using real quantum computer hardware have been reported yet, and
all existing reports rely on quantum computer emulators running on classical
machines. For example, Benenti et al. performed calculations using a simplified
potential function \cite{Benenti2008.10.1119/1.2894532}. Chan et al. utilized
both a quantum computer emulator and a classical program, processing the Coulomb
potential calculations on the classical side \cite{Chan2023.sciadv.abo7484}. In
other words, an example of computing the Coulomb potential entirely within a
quantum circuit has not yet been reported, even on an emulator. Therefore, in
this study, we present the configuration and operational demonstration of a
grid-based simulator implemented entirely with quantum circuits, including the
Coulomb potential calculation. The software used to generate the simulator
circuits is crsQ, developed by the author
\cite{takahashi2024.doi:10.1021/acs.jctc.4c00708}. We implement the wave
function time evolution calculation via the grid method entirely as a quantum
circuit, execute it on a quantum computer emulator, and evaluate the
computational results. To achieve this, we address the following three
challenges.

The first challenge is to present a circuit configuration that can operate on an
emulator with a limited number of qubits. In this study, we simplify the
computational model to fit within the emulator's constraints, targeting 1D and
2D models of a single hydrogen atom with fixed nuclear coordinates. For the
Coulomb potential calculation, in addition to a method based on binary
arithmetic operations, we utilize Uniformly Controlled Rotation Z (UCRZ)
circuits \cite{Mottonen2004.PhysRevLett.93.130502}---which are similar to QROM
\cite{Babbush_2018b.PhysRevX.8.041015}---to reduce the required number of qubits.
The standard Suzuki-Trotter decomposition is employed for the time evolution
calculation \cite{Zalka-rspa.1998.0162}. Through this, we provide an example of
a circuit configuration executable on an emulator, which will serve as a
foundation for basic evaluations on early-stage FTQCs.

The second challenge is to determine the handling of the singularity (pole) of
the Coulomb potential. In the grid method, it is necessary to calculate the
potential energy for all possible combinations of coordinates for all particles
and obtain the product of the wave function amplitudes. The point where the
coordinates of the nucleus and the electron coincide is a singularity of the
Coulomb potential function, where the value diverges if left unaddressed. In
this study, we propose a method to determine an effective potential value based
on the geometric average of the potential within a minute local region
containing the singularity, and we verify its validity through numerical
evaluation.

The third challenge is to establish a method for determining simulation
parameters that minimize errors within a given number of qubits. In the grid
method, it is first necessary to determine the spatial resolution (grid spacing)
and the size of the simulation domain as simulation parameters. Furthermore,
when using the Suzuki-Trotter decomposition, the step size for time evolution
must also be defined. In this study, we present an integrated approach that
optimizes spatial parameters based on the tradeoff between spatial
discretization error and domain truncation error, and determines the temporal
parameters based on the requirements of the sampling theorem.

\end{document}